Uncertainty on the galaxy-halo connection for Lyman-$\alpha$ emitters at $z=3.1$

### 2016-04-02 paper/ms.tex
updated ms with new plot
caption figure 4

The preferred $1-\sigma$ range for the masses is $9.6<\log \mmin<11.0$
and $10.9<\log\mmax<13.0$.
\focc\ is completely determined by \mmin\ from \focc$=$0.015 when
$\log\mmin=9.6$ to $\focc=0.30$ when $\log\mmin=11.0$. 
We compute the power-law dependece between \focc\ and \mmin\ to be 
\begin{equation}
\focc = 0.1\left(\frac{\mmin}{10^{10.5}\hMsun}\right)^{0.93}.
\end{equation}
We remind to the reader that models whith $\log \focc>0.00$ ($\focc>1$)
correspond to cases where the halo number density is smaller 
than the number of observed LAEs but are  still consistent because of
the uncertainty in the median number density of LAEs in the universe
due to cosmic variance (see Fig. \ref{fig:cosmicv0} and
\S\ref{subsec:explore}).

\begin{figure}
\includegraphics[width=0.47\textwidth]{mmin_mmed_colordm.png}
\caption{ $\log M_{\rm min}$ vs $\log M_{\rm 50\%}$ (black), $\log
  M_{\rm 16\%}$-$\log M_{\rm 84\%}$ (blue) and  $\log M_{\rm
    2.5\%}$-$\log M_{\rm 97.5\%}$(red) for different values of $\log
  M_{\rm max}$. The points are color coded by $\Delta \log
  M\left[\rm{M_{\odot}h^{-1} ]}\right]$. The green line diagonal line
accounts for the 1:1 relation and the green vertical lines represent
the 16, 50 and 84 percentiles  of the posterior probability
distribution of \mmin.} 
\label{fig:mmed}
\end{figure}

>>>>

The preferred $1-\sigma$ range for the masses is $9.6<\log \mmin<11.0$
and $10.9<\log\mmax<13.0$.
\focc\ is completely determined by \mmin\ from \focc$=$0.015 when
$\log\mmin=9.6$ to $\focc=0.30$ when $\log\mmin=11.0$. 
We compute the power-law dependece between \focc\ and \mmin\ to be 
\begin{equation}
\focc = 0.1\left(\frac{\mmin}{10^{10.5}\hMsun}\right)^{0.93}.
\end{equation}
We remind the reader that models whith $\log \focc>0.00$ ($\focc>1$)
correspond to cases where the halo number density is smaller 
than the number of observed LAEs but are  still considered consistent
because of the expected uncertainty in the median number density of
LAEs due to cosmic variance (see Fig. \ref{fig:cosmicv0} and
\S\ref{subsec:explore}).

\begin{figure}
\includegraphics[width=0.47\textwidth]{fig4.pdf}
\caption{Median mass, $\log M_{50}$, and mass width $\Delta
  M_{1\sigma}=\log M_{84} - \log M_{16}$, for all models with low
  $\chi^2_{\mathcal{M}}/2 < 1.0$. The median mass spans two orders of
  magnitude with a mean value around $10^{10.5}$\hMsun. The
  width has a median of $0.3$ dex (a factor of $2$ in
  mass) with a maximum value of $0.7$ dex (a factor of 5). This means
  that all models consistent with observations have a very narrow
  range in halo mass where the LAEs are expected to be hosted.} 
\label{fig:mmed}
\end{figure}
